All watched over by machines of loving grace

### 2021-06-24 paper/paper.tex
paper: added Nick as an author, reorganized the paper's structure

\title{All watched over by machines of loving grace}
\author{Dominic P. Mulligan}
\date{Systems Research Group, Arm Research, Cambridge}

@@

\section{Supervisionary}
\label{sect.supervisionary}

\subsection{Logic}
\label{subsect.logic}

@@

\subsection{The kernel runtime state}
\label{subsect.the.kernel.runtime.state}

@@

>>>>

\title{All watched over by machines of loving grace}
\author{Dominic P. Mulligan and Nick Spinale}
\date{Systems Research Group, Arm Research, Cambridge}

@@

\paragraph{Contributions}
We make the following contributions in this paper:

\begin{enumerate}
\item
We design a proof-checking kernel for Gordon's HOL structured around a series of tables of kernel objects indexed by handles.
With this, we introduce \emph{Supervisionary}, a prototype interactive theorem proving system which exposes its kernel as an ABI to WebAssembly programs.
\item
Noting that Supervisionary is little other than an exercise in pointer manipulation, we briefly explore how our ABI can be formally specified, using a variant of Separation Logic.
\item
We exploit Supervisionary's proof checking capabilities to define expressive dynamic security policies for WebAssembly programs.
\end{enumerate}

The remainder of the paper is structured as follows.
In Section~\ref{sect.gordons.hol} we briefly introduce Gordon's HOL.
In Section~\ref{sect.design.supervisionary.kernel} we describe the design of the Supervisionary kernel.
In Section~\ref{sect.supervisionary.system} we describe the Supervisionary system proper, including untrusted support code---the analogue of Unix's \texttt{libc}---that allows WebAssembly programs to interact with the kernel.
In Section~\ref{sect.separation.logic.an.interlude} we briefly explore how Separation Logic can be used to provide a formal description of the action of the Supervisionary ABI.
In Section~\ref{sect.security.policies.for.webassembly} we show how expressive security policies can be captured, and enforced, for arbitrary WebAssembly programs using Supervisionary.
Finally, in Section~\ref{sect.conclusions} we conclude.

\section{Gordon's HOL}
\label{sect.gordons.hol}

@@

\section{The design of the Supervisionary kernel}
\label{sect.design.supervisionary.kernel}

@@

\section{The Supervisionary system}
\label{sect.supervisionary.system}

\section{Separation Logic: an interlude}
\label{sect.separation.logic.an.interlude}

\section{Security policies for WebAssembly}
\label{sect.security.policies.for.webassembly}

\section{Conclusions}
\label{sect.conclusions}
